\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png} \\ {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-5mm}

### 2024-01-19 text/paper/paper.tex

\title{\vspace{-13mm}\includegraphics[width=15mm,scale=3]{images/IST_Logo.png}
% \\ \vspace{1mm} LFEUI \vspace{1mm} 
\\ {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-5mm}}
\date{December 2023 - January 2024}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.15]{images/scheme.jpeg}
    \captionof{figure}{Experimental Set-up}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.17]{images/Li_crosssection_energy.jpeg}
    \captionof{figure}{Cross section of the reaction between protons and Li-7 as a function of the beam energy}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.35]{images/Calib.png}
    \captionof{figure}{Spectrum of the Calibration source}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.6]{images/TT_21_Chn0.png}
    \captionof{figure}{Channel 0 spectrum fit with [\ref{eq:califit}]}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.35]{images/Chn0_calib_with_Backscattering.png}
    \captionof{figure}{Calibration "detector 0"}
\end{center}

@@

\begin{center}
    \label{alfa_peaks}
    \centering
    \includegraphics[scale = 0.35]{images/AlphaPeaks.png}
    \captionof{figure}{Theoretical energy values of the two alfphas}
\end{center}

The energies obtained were 7629.80 kEv and 11031.44 kEv. (FALTA EXPLICAR PERCENTAGENS)

@@

For the LiF sample, we overlapped the expected $\alpha$ energy getting the following spectrum:

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.35]{images/OverlapLiF_NC.png}
    \captionof{figure}{Spectrum of the $\ce{LiF}$ sample}
\end{center}

The experimental $\alpha_0$ is extremely close to the theoretical value, therefore we can confirm the presence of lithium in this sample. Analysing this spectrum further:

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.4]{images/FullAnalysisLiF.png}
    \captionof{figure}{Spectrum of the $\ce{LiF}$ sample}
\end{center}

There are three noticeable structures in this spectrum. 
The first one is a peak around channel 0, followed by a less intense one around 100 Chn and a small plateau between 150 and 250 Chn. 
Lastly, there is an evident energy profile that starts at around 300 Chn and goes up to 900 Chn with increasing intensity.

\paragraph*{}

After identifying these structures we used the previous calibration [\ref{sec:calibration}] to convert the channel values into energy values so that we could more effectively analyse the spectrum and its peaks.

@@

We obtained the following spectrum for the lithium aluminate sample:

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.35]{images/OverlapLiAlO2.png}
    \captionof{figure}{Spectrum of the $\ce{LiAlO_2}$ sample}
\end{center}

@@

The obtained spectrum for the implanted sample was the following:

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.35]{images/OverlapImplanted.png}
    \captionof{figure}{Spectrum of the implanted sample}
\end{center}

>>>>

\title{\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}
% \\ \vspace{1mm} LFEUI \vspace{1mm} 
\\ {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-5mm}}
\date{December 2023 - January 2024}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.15]{../images/scheme.jpeg}
    \captionof{figure}{Experimental Set-up}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.17]{../images/Li_crosssection_energy.jpeg}
    \captionof{figure}{Cross section of the reaction between protons and Li-7 as a function of the beam energy}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.35]{../../images/Calib.png}
    \captionof{figure}{Spectrum of the Calibration source}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.6]{../../images/TT_21_Chn0.png}
    \captionof{figure}{Channel 0 spectrum fit with [\ref{eq:califit}]}
\end{center}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.35]{../../images/Chn0_calib_with_Backscattering.png}
    \captionof{figure}{Calibration "detector 0"}
\end{center}

@@

\begin{center}
    \label{alfa_peaks}
    \centering
    \includegraphics[scale = 0.35]{../../images/AlphaPeaks.png}
    \captionof{figure}{Theoretical energy values of the two alfphas}
\end{center}

The energies obtained were 7629.80 kEv and 11031.44 kEv. (FALTA EXPLICAR PERCENTAGENS)
For the identification of lithium in our samples, we need to compare the theoretical energy values with the experimental ones.
Since we know the the emited alpha in our samples is more energetic than the theoretical values, it is expected that the experimental peaks are slightly higher than the theoretical ones.
If the seamples contains a peak in the proximity of the alpha peaks it shows that the sample contains lithium.

@@

For the LiF sample, we used the calibration [\ref*{sec:calibration}] to convert the channel values into energy values.
we overlapped the expected $\alpha$ energy with the spectrum, and obtained the following:

\begin{center}
    \centering
    \includegraphics[scale = 0.35]{../../images/OverlapLiF_NC.png}
    \captionof{figure}{Spectrum of the $\ce{LiF}$ sample}
\end{center}

The experimental $\alpha_0$ is extremely close to the theoretical value, therefore we can confirm the presence of lithium in this sample. 
Moreover, it is according to the expected hyphotesis that the observed lithium energy is slightly higher than the theoretical value.
Analysing this spectrum further:

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.4]{../../images/FullAnalysisLiF.png}
    \captionof{figure}{Full Analysis of $\ce{LiF}$ Spectrum}
\end{center}

There are three noticeable structures in this spectrum. 
The first one is a peak around 0 keV, which is just electronic noise. The following structure is backscattering, identified by the barrier of 1146.5 kEv. 
The backscattering is followed by event pile-up, which is the energy profile referenced in section \ref{sec:energy_profile_peak}.

@@

We used the calibration again to obtain the Lithium Alimunate energy spectrum overlapped with the expected $\alpha$ energy:

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.35]{../../images/OverlapLiAlO2.png}
    \captionof{figure}{Spectrum of the $\ce{LiAlO_2}$ sample}
\end{center}

The experimental $\alpha_0$ is very similar to the theoretical value, hence we can confirm the presence of lithium in this sample. 
If we analyse this spectrum further, we can see the following:

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.4]{../../images/FullAnalysisLiAlO2.png}
    \captionof{figure}{Full Analysis of $\ce{LiAlO_2}$ Spectrum}
\end{center}

It is evident that the structure of the spectrum follows a similar pattern to the one in the previous sample.
First, there is electrical noise, followed by backscattering and event pile-up. 
The backscattering is identified by the barrier of 1150.0 kEv.

@@

Finally, we used the calibration to obtain the implanted sample energy spectrum overlapped with the expected $\alpha$ energy:
\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.35]{../../images/OverlapImplanted.png}
    \captionof{figure}{Spectrum of the implanted sample}
\end{center}

There is a peak in the proximity of the $\alpha_0$ peak, which is the expected lithium peak.
One more time we can confirm the presence of lithium in this sample.

If we analyse the spectrum further:

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.4]{../../images/FullAnalysisImplanted.png}
    \captionof{figure}{Full Analysis of the Implanted Sample Spectrum}
\end{center}
